---
title: "STAT 2260 Homework 1"
author: "Jihang Jiang"
date: "2023-09-11"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Objects (13 points)

A user has typed the following commands into the console.

#### 1) Show the value of each object and use R command to measure the length of them. (4 points)

```{r}
obj1 <- seq(-3,21,3)
obj2 <- c(1,3,5)
obj3 <- obj2>2.5
obj4 <- "I love pizza."
```

```{r}
obj1
```

```{r}
length(obj1)
```

```{r}
obj2
```

```{r}
length(obj2)
```

```{r}
obj3
```

```{r}
length(obj3)
```

```{r}
obj4
```

```{r}
length(obj4)
```

#### 2) What values are returned by the following commands? (9 points)

```{r}
obj1*(-1)
```

```{r}
obj1[2:6]
```

```{r}
obj1[-2]
```

```{r}
obj1 + obj2
```

```{r}
obj1 * obj3
```

```{r}
obj2 + obj3
```

```{r}
#obj1+obj4 #obj4 is a character type, obj1 is numeric type.
```

```{r}
sum(obj2)
```

```{r}
sum(obj3)
```

### 2. Vectors (5 points)

A user has typed the following commands into the console.

```{r}
a <- c(0, 1)
b <- c(TRUE, FALSE)
c <- c("happy", "sad")
```

What do each of the following commands return? Pay attention to the type of the vector after concatenating two or more vectors.

```{r}
a+b
```

```{r}
a*b
```

```{r}
d <- c(a,b);d
```

```{r}
e <- c(a,c);e
```

```{r}
g <- c(b,c);g
```

```{r}
w <- c(a,b,c);w
```

### 3. Errors (5 points)

For each of the following assignment statements, describe the error (or note why it does not generate an error).

1.The function should be floor(), we should put 10.3 into parentheses.

```{r}
#result1 <- floor 10.3 
```

2.It should be \<- not \<--

```{r}
#result2 <-- "Hello to you!"
```

3.Variable names should not start with a number.

```{r}
#3result <- "Hello to you"
```

4.Missing a " on right side.

```{r}
#result4 <- "Hello to you
```

5.Correct! The date() function is used to get the current system date and time. This function doesn't take any parameters.

```{r}
#result5 <- date()
```

### 4. Matrices (7 points)

##### 1) (4 points) Create two matrices as follows by writing code. Call them `M1` and `M2`, respectively.

```{r}
m1 <- c(24, 22, 20, 18, 16, 14, 12, 10, 8, 6, 4, 2)
M1 <- matrix(m1,3,4)
M2 <- matrix(m1,3,4,byrow = TRUE)

```

```{r}
M1
```

```{r}
M2
```

2)  Extract the value at the 3nd row and 1st column of M1 using R (1 points)

```{r}
M1[3,1]
```

3)  Extract the values in the 2nd row in M1 using R (1 points)

```{r}
M1[2,]
```

4)  Extract the values in the 3nd column in M2 using R (1 points)

```{r}
M2[,3]
```

### 5.Calculate the following using R (5 points)

##### 1) $log_{10}(1)-ln(1)$

```{r}
log10(1)-log(1)
```

##### 2) $sin(\pi/3)$+cos$(\pi/3)$

```{r}
sin(pi/3)+cos(pi/3)
```

##### 3) Round up the result of 2) to the nearest integer

```{r}
floor(sin(pi/3)+cos(pi/3))
```

##### 4) Round the result of 2) to two decimal places

```{r}
round(sin(pi/3)+cos(pi/3),2)
```

##### 5) Calculate the remainder of $2022/9$ using R

```{r}
2022 %% 9
```

### 6. Data Frames (15 points)

##### 1) Create a data frame as follows (4 points):

```{r}
name <- c("Jacob","James","Jeremy","Jimmy","John")
year <- c(1,2,3,4,3)
gpa <- c(3.41, 3.53, 3.32, 3.67, 4.00)
height <- c(1.78, 1.85, 1.72, 1.82, 1.68)
df <- data.frame("Name"=name,"Year"=year,"GPA"=gpa,"Height"=height);df
```

##### 2) Use the column name to extract the GPA of all students. (2 points)

```{r}
df$GPA
```

##### 3) Select the information about Jeremy (2 points).

```{r}
df[3,]
```

##### 4) List name(s) of students whose GPA is lower than 3.6 (3 points).

```{r}
df[df$GPA<3.6,1]
```

##### 5) List the GPA of all 3rd-year students and calculate the mean GPA. (4 points)

```{r}
gpa_3rd <- df[df$Year==3,3];gpa_3rd
```

```{r}
mean(gpa_3rd)
```
