---
title: "STAT 2260 Homework 4"
author: "Jihang Jiang"
date: "2023-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(Hmisc)
library(mdsr)
library(dplyr)
library(babynames)

```

```{r}
BabynamesDist <- make_babynames_dist()
head(BabynamesDist)
```

 

```{r}
anna_data <- BabynamesDist %>%
  filter(name=="Anna") 
summary(anna_data);anna_data
```
## Q1

#### Estimate the values of the three summary statistics (Q1, Median, Q3) for Anna in the data graphic.

#### Answer: Estimated Q1: 14, estimated median: 32, estimated Q3:61 


## Q2

#### Which name(s) has(have) the smallest inter-quartile range for age?

#### Answer: Jessica, Lisa



## Q3

#### According to what summary statistic are the names ordered in the figure?


#### Answer: Names in the figure is ordered by median_age.

## Q4

#### List four visual cues that were used in this visualization.

#### Answer: geom_linerange, geom_point, geom_text, ggtitle

## Q5

#### Create a new variable with value \|0.5−boys/total\|, using mutate(). List the top 10 years in which the name "Taylor" was given to M and F babies most equally.

```{r}
babynames %>%
  filter(name=="Taylor") %>%
  group_by(year) %>%
  summarise(
    N= n(),
    total = sum(n),
    boys = sum(ifelse(sex=="M",n,0))
  ) %>%
  mutate(new_variable = abs(0.5-boys/total)) %>%
  arrange(new_variable) %>%
  head(10)
```

## Q6

#### Re-create the data graphic, "Youngest Male Names" (again, your result will be different from the chart below).

```{r}
young_data <- BabynamesDist %>%
  filter(sex =="M", est_alive_today>0) %>%
  group_by(name) %>%
  summarise(
    est_num_alive = sum(est_alive_today),
    q1_age = wtd.quantile(age_today, est_alive_today, 0.25),
    median = wtd.quantile(age_today, est_alive_today, 0.5),
    q3_age = wtd.quantile(age_today, est_alive_today, 0.75)
  )%>%
  filter(est_num_alive>100000)%>%
  arrange(median)%>%
  head(25)
young_data
```


```{r}
m_plot <- ggplot(
  data = young_data, 
  aes(x = reorder(name, -median),  y = median)) + 
  xlab(NULL) + 
  ylab("Age (in years)")
m_plot<- m_plot+
  geom_linerange(
    aes(ymin=q1_age,ymax=q3_age),
    color="#87cefa",
    linewidth=4,
    alpha=0.8
  )+
  geom_point(fill = "#ed3324", colour = "white", size = 3, shape = 21) +
  geom_point(aes(y=25,x=23.5),fill = "#ed3324", colour = "white", size = 3, shape = 21) +
  geom_text(aes(y=27,x=23.5),label="median",cex=3.8)+
  geom_text(aes(y=9.5,x=11),label="25th",cex=3.8)+
  geom_text(aes(y=16.5,x=11),label="75th percentile",cex=3.8)+
  geom_point(aes(y=8.5,x=11),shape=17)+
  geom_point(aes(y=18.5,x=11),shape=17)+
  labs(title ="Youngest Male Names" , subtitle = "By estimated median age for Americans alive as of Jan.1,2014")+
  coord_flip()
m_plot
```

### Use babynames data set to answer the following questions. Think carefully about what data transformations are needed to answer each question.

## Q7

#### Which year had the highest number of births?

#### 1957 had the hightest number of births

```{r}
babynames %>%
  group_by(year)%>%
  summarise(
    N=n(),
    birth_num = sum(n)
  ) %>%
  arrange(desc(birth_num))
```

## Q8

#### Find the most popular girl name between 1990 and 2000 (including 1990 and 2000).

#### Answer: the most popular girl name between 1990 and 2000 is "Ashley"

```{r}
babynames %>%
  group_by(name) %>%
  filter(year>=1990 , year<=2000 , sex=="F")%>%
  summarise(
    N=n(),
    name_sum = sum(n)
  )%>%
  arrange(desc(name_sum))
```