---
title: "HW5_STAT2260"
author: "Jihang Jiang"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(kableExtra)
library(tidyverse)

ebsurvey <- read_csv('science-faith-attitude.csv')
head(ebsurvey)
```
```{r}
ebsurvey0 <- ebsurvey %>% 
  select(kstot, age, toomuchscience)
```

```{r}
ebsurvey0 <- ebsurvey0 %>% 
  rename(science_score = kstot,
         attitude = toomuchscience)
head(ebsurvey0,3)
```
```{r}
ebsurvey1 <- na.omit(ebsurvey0)
dim(ebsurvey1)
```
## Exercise 1. (15 points) Explore the distribution of science knowledge quiz scores
(5 points) Create a histogram for science_socre. Overlay the histogram with a density curve.

(10 points) Create a summary statistics table for science_score. Note that you need to calculate the mean, standard deviation, median, Q1, Q3, and the range of it.

```{r}
ggplot(ebsurvey1, aes(x = science_score,y=after_stat(density))) +
    geom_histogram(color = 'white', fill='steelblue',binwidth = 1) +
    labs(x = 'science_socre', 
         y = 'Frequency') +
    geom_density(size=1.5)
```

```{r}
ebsurvey1 %>%
    summarise(Mean = mean(science_score),
              SD = sd(science_score),
              Median = quantile(science_score, 0.5),
              Q1 = quantile(science_score, 0.25),
              Q3 = quantile(science_score, 0.75),
              Range = max(science_score)-min(science_score)) %>%
    kable(digits = 2, 
          caption = 'Descriptive Statistics of Science_score') %>%
    kable_styling(full_width = FALSE)
```

## Exercise 2. Use the functions in Lecture 14 to do bootstrap for regression for this problem. Use 100 bootstrap samples.

Requirement: Calculate a 99% confidence interval for each term.


```{r}
library(broom)
library(modelr)
library(purrr)
```



```{r}
boot <- modelr::bootstrap(ebsurvey1,100)
models <- map(boot$strap,~lm(attitude ~ science_score + age, data=.))
models.tb <- map_df(models,broom::tidy,.id="id")
```

```{r}
head(models.tb)
```

```{r}
models.tb %>% 
  filter(term=="(Intercept)") %>% 
  summarize(LowerBound_Intercept=quantile(estimate,0.005),UpperBound_Intercept=quantile(estimate,0.995))
```


```{r}
models.tb %>% 
  filter(term=="science_score") %>% 
  summarize(LowerBound_science_score=quantile(estimate,0.005),UpperBound_science_score=quantile(estimate,0.995))
```

```{r}
models.tb %>% 
  filter(term=="age") %>% 
  summarize(LowerBound_age=quantile(estimate,0.005),UpperBound_age=quantile(estimate,0.995))
```
## Exercise 3. (15 points) Create a visualization for the bootstrap sample you got in Exercise 2.

Requirements:

Create a histogram for each coefficient.

Overlay (kernel) density curves on the histograms. (Hint: Use geom_density)

Display all three histograms in one plot. (Hint: Use facet_wrap)


```{r}
coe_plot <- ggplot(models.tb,aes(x=estimate,y=after_stat(density)))+
  geom_histogram(fill="steelblue",bins = 15)+
  geom_density(size=1)+
  facet_wrap(~ term,scales = "free")
coe_plot
```

























